Location and Scale-Invariant Power Transformations for Transforming Data to

### 2024-09-05 manuscript/manuscript.Rmd
Additional improvements to manuscript.

Many statistical and several machine learning methods assume normality of the underlying data, e.g. analysis of variance or . However, numerical features in datasets may strongly deviate from normal distributions, e.g. by being skewed. Power transformations aim to stabilise variance and improve normality of such features [@Bartlett1947-rx; @Tukey1957-rt]. The two most commonly used transformations are that of @Box1964-mz and @Yeo2000-vw. The Box-Cox transformation of a feature value $x_i$ of feature $\mathbf{X}=\left\{x_1, x_2, \ldots, x_n \right\}$ under the transformation parameter $\lambda$ is defined as:

@@

Power transformation does not guarantee that transformed features are normally distributed.
Depending on location and scale of a feature and the presence of outliers, power transformation may decrease normality, as shown in Figure \ref{fig:decreased-normality}.
If normality of the transformed feature is not checked, e.g. in automated power transformation in machine learning workflows, several issues may arise.
For example, statistical tests such as ANOVA may produce incorrect results due to violation of the normality assumption.
Likewise, machine learning methods that assume normality of input features may suffer a decrease in performance.
Also, large negative or positive $\lambda$-parameters may lead to numeric issues in any subsequent computations.

@@

```{=latex}
\begin{equation}
\label{eqn:box-cox-invariant-log-likelihood}
\begin{split}
\mathcal{l}_{\text{BC}}^{\lambda, x_0, s} = & -\frac{n}{2} \log \left[2 \pi \sigma^2 \right] -\frac{1}{2 \sigma^2} \sum_{i=1}^n \left( \phi_{BC}^{\lambda, x_0, s}(x_i) - \mu \right)^2 \\
& -n \lambda \log s + \left( \lambda - 1 \right) \sum_{i=1}^n \log \left[ x_i - x_0 \right]
\end{split}
\end{equation}
```
where $\mu$ and $\sigma^2$ are the mean and variance of the Box-Cox transformed feature $\phi_{\text{BC}}^{\lambda, x_0, s} (\mathbf{X})$, respectively.
Similarly, the location- and scale-invariant Yeo-Johnson log-likelihood function is:

```{=latex}
\begin{equation}
\label{eqn:yeo-johnson-invariant-log-likelihood}
\begin{split}
\mathcal{l}_{\text{YJ}}^{\lambda, x_0, s} = & -\frac{n}{2} \log\left[2 \pi \sigma^2\right] -\frac{1}{2 \sigma^2} \sum_{i=1}^n \left( \phi_{YJ}^{\lambda, x_0, s}(x_i) - \mu \right)^2 \\
& - n \log s + (\lambda - 1) \sum_{i=1}^n \sgn(x_i - x_0) \log \left[1 + \frac{|x_i - x_0|}{s} \right]
\end{split}
\end{equation}
```
where $\mu$ and $\sigma^2$ are the mean and variance of the Box-Cox transformed feature $\phi_{\text{YJ}}^{\lambda, x_0, s} (\mathbf{X})$, respectively.

@@

```{=latex}
\begin{equation}
\label{eqn:box-cox-weighted-invariant-log-likelihood}
\begin{split}
\mathcal{l}_{\text{rBC}}^{\lambda, x_0, s} = & -\frac{1}{2} \left(\sum_{i=1}^n w_i \right) \log \left[ 2 \pi \sigma_w^2 \right] -\frac{1}{2 \sigma_w^2} \sum_{i=1}^n w_i \left( \phi^{\lambda, x_0, s}(x_i) - \mu_w \right)^2 \\
& - \lambda \left( \sum_{i=1}^n w_i \right) \log s + \left( \lambda - 1 \right) \sum_{i=1}^n w_i \log \left[ x_i - x_0 \right]
\end{split}
\end{equation}
```
where $\mu_w$ and $\sigma^2_w$ are the weighted mean and weighted variance of the Box-Cox transformed feature $\phi_{\text{BC}}^{\lambda, x_0, s} (\mathbf{X})$:

```{=latex}
\begin{equation}
\sigma_w^2 = \frac{\sum_{i=1}^n w_i \left(\phi_{\text{BC}}^{\lambda, x_0, s} (x_i) - \mu_w \right)^2}{\sum_{i=1}^n w_i} \quad \text{with } \mu_w = \frac{\sum_{i=1}^n \phi_{\text{BC}}^{\lambda, x_0, s} (x_i)} {\sum_{i=1}^n w_i}
\end{equation}
```

@@

```{=latex}
\begin{equation}
\label{eqn:yeo-johnson-weighted-invariant-log-likelihood}
\begin{split}
\mathcal{l}_{\text{rYJ}}^{\lambda, x_0, s} = & -\frac{1}{2} \left(\sum_{i=1}^n w_i \right) \log \left[ 2 \pi \sigma_w^2 \right] -\frac{1}{2 \sigma_w^2} \sum_{i=1}^n w_i \left( \phi^{\lambda, x_0, s}(x_i) - \mu_w \right)^2 \\
& - \left( \sum_{i=1}^n w_i \right) \log s + (\lambda - 1) \sum_{i=1}^n w_i \sgn(x_i - x_0) \log \left[1 + \frac{|x_i - x_0|}{s} \right]
\end{split}
\end{equation}
```
where $\mu_w$ and $\sigma^2_w$ are the weighted mean and weighted variance of the Yeo-Johnson transformed feature $\phi_{\text{YJ}}^{\lambda, x_0, s} (\mathbf{X})$:

```{=latex}
\begin{equation}
\sigma_w^2 = \frac{\sum_{i=1}^n w_i \left(\phi_{\text{YJ}}^{\lambda, x_0, s} (x_i) - \mu_w \right)^2}{\sum_{i=1}^n w_i} \quad \text{with } \mu_w = \frac{\sum_{i=1}^n \phi_{\text{YJ}}^{\lambda, x_0, s} (x_i)} {\sum_{i=1}^n w_i}
\end{equation}
```

The weights $w_i$ in equations \ref{eqn:box-cox-weighted-invariant-log-likelihood} and \ref{eqn:yeo-johnson-weighted-invariant-log-likelihood} can be set using several weighting functions.
Here, we investigate three:

@@

- The weighting function uses empirical probabilities of the distribution of the original feature $\mathbf{X}$.
  Probabilities are determined as $p_i = \frac{i - 1/3}{n + 1/3}$, with $i = 1, 2, \ldots n$, with $n$ the number of instances of feature $\mathbf{X}$.
  Then $\dot{x}_i = p^{*}_i=2 \left( p_i - 0.5\right)$, so that argument is zero-centered.

@@

- The weighting function uses the residual error between the z-score of the transformed feature $\phi^{\lambda, x_0, s} (\mathbf{X})$ and the theoretical z-score from a standard normal distribution: $r_i =\left| \left( \phi^{\lambda, x_0, s}(x_i) - \mu_M)\right) / \sigma_M - F^{-1}_{\mathcal{N}}(p_i) \right|$, with $\mu_M$, $\sigma_M$ and $p_i$ as defined above.
  Then $\dot{x}_i = r_i$.

@@

```{=latex}
\begin{equation}
f_{\beta}(x) = \frac{\beta}{2\Gamma \left(1 / \beta \right)} e^{-\left| x \right|^\beta}
\end{equation}
```
Here, $\Gamma$ is the gamma function, and $\beta$ is a strictly positive shape parameter. For $\beta = 1$, the probability density function describes a Laplace distribution. A normal distribution is found for $\beta=2$, and for large $\beta$, the distribution approaches a uniform distribution. We will refrain from introducing scale and location parameters here directly.

@@

```{=latex}
\begin{equation}
F_{\alpha}^{-1}(p; \mu, \sigma, \beta) =
\begin{cases}
\mu + \frac{\sigma}{1 - \alpha} F_{\beta}^{-1} \left( \frac{p}{2 \alpha}\right) & \text{, } p \leq \alpha \\
\mu + \frac{\sigma}{\alpha} F_{\beta}^{-1} \left( \frac{1 + p - 2 \alpha}{2 \left(1 - \alpha \right)} \right) & \text{, } p > \alpha
\end{cases}
\end{equation}
```
The quantile function for the asymmetric generalised normal distribution $F_{\alpha}^{-1}(p)$ thus incorporates the quantile function $F_{\beta}^{-1}(p^{*})$ of the symmetric generalised normal distribution. $F_{\beta}^{-1}(p)$ was derived by Griffin to be [@Griffin2018-bf]:

@@

Let central normality be defined as normality of central portion $\kappa$ of the data, i.e. $\mathbf{X}_{\text{central}} = \left\{x_i \in \mathbf{X} \, | \,  \frac{1-\kappa}{2} \leq  p_i \leq \frac{1 + \kappa}{2}\right\}$, with $p_i$ probabilities of the empirical distribution, as previously.
We then compute the residual errors between the z-scores of the transformed feature $\phi^{\lambda, x_0, s} (\mathbf{X})$ and the expected z-scores from a standard normal distribution: $r_i =\left| \left( \phi^{\lambda, x_0, s}(x_i) - \mu_M)\right) / \sigma_M - F^{-1}_{\mathcal{N}}(p_i) \right|$, with $\mu_M$ and $\sigma_M$ robust Huber M-estimates of location and scale of the transformed feature $\phi^{\lambda, x_0, s} (\mathbf{X})$ [@Huber1981-su].
The set of residual errors for the central portion of the data is then $\mathbf{R}_{\text{central}} = \left\{ r_i \in \left\{ r_1, r_2, \ldots, r_n\right\} \, | \,  \frac{1-\kappa}{2} \leq  p_i \leq \frac{1 + \kappa}{2}\right\}$.

@@

@@

We used simulated data to assess invariance to location and scale of the proposed power transformations, weighting for robust transformations, and to develop the empirical central normality test.
The $\lambda$ parameter for conventional power transformations (Eqn. \ref{eqn:box-cox-original} and \ref{eqn:yeo-johnson-original}), as well as $\lambda$, $x_0$ and $s$ parameters for location- and scale-invariant power transformations (Eqn. \ref{eqn:box-cox-invariant} and \ref{eqn:yeo-johnson-invariant}) were estimated using the BOBYQA algorithm for derivative-free bound constraint optimisation [@Powell2009-zb] through maximum likelihood estimation.

@@

To assess whether the proposed power transformations lead to values of $\lambda$ that are invariant to location and scale of the distribution, we simulated three different distributions.
We first randomly drew $10000$ values from a normal distribution: $\mathbf{X}_{\text{normal}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{N}\left(0, 1\right)$, or equivalently $\mathbf{X}_{\text{normal}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.5, 2\right)$.
The second distribution was a right-skewed normal distribution $\mathbf{X}_{\text{right}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.2, 2\right)$.
The third distribution was a left-skewed normal distribution $\mathbf{X}_{\text{left}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.8, 2\right)$.
We then computed transformation parameter $\lambda$ using the original definitions (equations \ref{eqn:box-cox-original} and \ref{eqn:yeo-johnson-original}) and the location- and scale-invariant definitions (equations \ref{eqn:box-cox-invariant} and \ref{eqn:yeo-johnson-invariant}) for each distribution.
To assess location invariance, a positive value $d_{\text{shift}}$ was added to each distribution with $d_{\text{shift}} \in [1, 10^6]$.
Similarly, to assess scale invariance, each distribution was multiplied by a positive value $d_{\text{scale}}$, where $d_{\text{scale}} \in [1, 10^6]$.

@@

Outlier values were then drawn to randomly replace a fraction of the values of $\mathbf{X}_i$.
This was repeated $m_{out} = 10$ times, with outlier fractions regularly spaced in $[0.00, 0.10]$.
Thus up to 10 percent of the values could be replaced by outliers.
Outlier values were set according to @Tukey1977-xm, as follows.
Let $x^{*} \sim U\left(-2, 2\right)$.
Then the corresponding outlier value was:

@@

$Q_1$, $Q_3$ and $\text{IQR}$ are the first quartile, third quartile and interquartile range of $\mathbf{X}_i$, respectively.
Outlier values randomly replaced values in $\mathbf{X}_i$ to create $\mathbf{X}_{i,j}$.

@@

```{=latex}
\begin{equation}
\label{eqn:minimisation-weighting}
\left\{ \hat{\delta}_1, \hat{\delta}_2 \right\} = \argmin_{\delta_1, \delta_2} \sum_{i=1}^{m_d} \sum_{j=1}^{m_{out}} \left| \lambda_r \left(\mathbf{X}_{i, j}; \delta_1, \delta_2 \right) - \lambda_0 \left(\mathbf{X}_i \right) \right|
\end{equation}
```

>>>>

Many statistical and some machine learning methods assume normality of the underlying data, e.g. analysis of variance and linear discriminant analysis.
However, numerical features in datasets may strongly deviate from normal distributions, e.g. by being skewed.
Power transformations aim to stabilise variance and improve normality of such features [@Bartlett1947-rx; @Tukey1957-rt].
The two most commonly used transformations are that of @Box1964-mz and @Yeo2000-vw.
The Box-Cox transformation of a feature value $x_i$ of feature $\mathbf{X}=\left\{x_1, x_2, \ldots, x_n \right\}$ under the transformation parameter $\lambda$ is defined as:

@@

Applying a power transformation does not guarantee that transformed features are normally distributed.
Depending on location and scale of a feature and the presence of outliers, power transformations may decrease normality, as shown in Figure \ref{fig:decreased-normality}.
If normality of the transformed feature is not checked, e.g. in automated power transformation in machine learning workflows, several issues may arise.
For example, statistical tests such as ANOVA may produce incorrect results due to violation of the normality assumption.
Likewise, machine learning methods that assume normality of input features may suffer a decrease in performance.
Moreover, large negative or positive $\lambda$-parameters may lead to numeric issues in any subsequent computations.

@@

```{=latex}
\begin{equation}
\label{eqn:box-cox-invariant-log-likelihood}
\begin{split}
\mathcal{l}_{\text{BC}}^{\lambda, x_0, s} = & -\frac{n}{2} \log \left[2 \pi \sigma^2 \right] -\frac{1}{2 \sigma^2} \sum_{i=1}^n \left( \phi_{BC}^{\lambda, x_0, s}(x_i) - \mu \right)^2 \\
& -n \lambda \log s + \left( \lambda - 1 \right) \sum_{i=1}^n \log \left[ x_i - x_0 \right]
\end{split}
\end{equation}
```
subject to $x_i - x_0 > 0$.
$\mu$ and $\sigma^2$ are the mean and variance of the Box-Cox transformed feature $\phi_{\text{BC}}^{\lambda, x_0, s} (\mathbf{X})$, respectively.
Similarly, the location- and scale-invariant Yeo-Johnson log-likelihood function is:

```{=latex}
\begin{equation}
\label{eqn:yeo-johnson-invariant-log-likelihood}
\begin{split}
\mathcal{l}_{\text{YJ}}^{\lambda, x_0, s} = & -\frac{n}{2} \log\left[2 \pi \sigma^2\right] -\frac{1}{2 \sigma^2} \sum_{i=1}^n \left( \phi_{YJ}^{\lambda, x_0, s}(x_i) - \mu \right)^2 \\
& - n \log s + (\lambda - 1) \sum_{i=1}^n \sgn(x_i - x_0) \log \left[1 + \frac{|x_i - x_0|}{s} \right]
\end{split}
\end{equation}
```
where $\mu$ and $\sigma^2$ are the mean and variance of the Yeo-Johnson transformed feature $\phi_{\text{YJ}}^{\lambda, x_0, s} (\mathbf{X})$, respectively.

@@

```{=latex}
\begin{equation}
\label{eqn:box-cox-weighted-invariant-log-likelihood}
\begin{split}
\mathcal{l}_{\text{rBC}}^{\lambda, x_0, s} = & -\frac{1}{2} \left(\sum_{i=1}^n w_i \right) \log \left[ 2 \pi \sigma_w^2 \right] -\frac{1}{2 \sigma_w^2} \sum_{i=1}^n w_i \left( \phi_{\text{BC}}^{\lambda, x_0, s}(x_i) - \mu_w \right)^2 \\
& - \lambda \left( \sum_{i=1}^n w_i \right) \log s + \left( \lambda - 1 \right) \sum_{i=1}^n w_i \log \left[ x_i - x_0 \right]
\end{split}
\end{equation}
```
where $\mu_w$ and $\sigma^2_w$ are the weighted mean and weighted variance of the Box-Cox transformed feature $\phi_{\text{BC}}^{\lambda, x_0, s} (\mathbf{X})$:

```{=latex}
\begin{equation}
\sigma_w^2 = \frac{\sum_{i=1}^n w_i \left(\phi_{\text{BC}}^{\lambda, x_0, s} (x_i) - \mu_w \right)^2}{\sum_{i=1}^n w_i} \quad \text{with } \mu_w = \frac{\sum_{i=1}^n w_i \phi_{\text{BC}}^{\lambda, x_0, s} (x_i)} {\sum_{i=1}^n w_i}
\end{equation}
```

@@

```{=latex}
\begin{equation}
\label{eqn:yeo-johnson-weighted-invariant-log-likelihood}
\begin{split}
\mathcal{l}_{\text{rYJ}}^{\lambda, x_0, s} = & -\frac{1}{2} \left(\sum_{i=1}^n w_i \right) \log \left[ 2 \pi \sigma_w^2 \right] -\frac{1}{2 \sigma_w^2} \sum_{i=1}^n w_i \left( \phi_{\text{YJ}}^{\lambda, x_0, s}(x_i) - \mu_w \right)^2 \\
& - \left( \sum_{i=1}^n w_i \right) \log s + (\lambda - 1) \sum_{i=1}^n w_i \sgn(x_i - x_0) \log \left[1 + \frac{|x_i - x_0|}{s} \right]
\end{split}
\end{equation}
```
where $\mu_w$ and $\sigma^2_w$ are the weighted mean and weighted variance of the Yeo-Johnson transformed feature $\phi_{\text{YJ}}^{\lambda, x_0, s} (\mathbf{X})$:

```{=latex}
\begin{equation}
\sigma_w^2 = \frac{\sum_{i=1}^n w_i \left(\phi_{\text{YJ}}^{\lambda, x_0, s} (x_i) - \mu_w \right)^2}{\sum_{i=1}^n w_i} \quad \text{with } \mu_w = \frac{\sum_{i=1}^n w_i \phi_{\text{YJ}}^{\lambda, x_0, s} (x_i)} {\sum_{i=1}^n w_i}
\end{equation}
```

The weights $w_i$ in equations \ref{eqn:box-cox-weighted-invariant-log-likelihood} and \ref{eqn:yeo-johnson-weighted-invariant-log-likelihood} can be set using several weighting functions. 
Using $\dot{x}_i$ as an argument that will be defined later, we investigate three weighting functions:

@@

- The weighting function uses empirical probabilities of the distribution of the original feature $\mathbf{X}$.
  After sorting $\mathbf{X}$ in ascending order, probabilities are determined as $p_i = \frac{i - 1/3}{n + 1/3}$, with $i = 1, 2, \ldots n$, with $n$ the number of instances of feature $\mathbf{X}$.
  Then $\dot{x}_i = p^{*}_i=2 \left( p_i - 0.5\right)$, so that argument is zero-centered.

@@

- After sorting $\mathbf{X}$ in ascending order, the weighting function uses the residual error between the z-score of the transformed feature $\phi^{\lambda, x_0, s} (\mathbf{X})$ and the theoretical z-score from a standard normal distribution: $r_i =\left| \left( \phi^{\lambda, x_0, s}(x_i) - \mu_M)\right) / \sigma_M - F^{-1}_{\mathcal{N}}(p_i) \right|$, with $\mu_M$, $\sigma_M$ and $p_i$ as defined above.
  Then $\dot{x}_i = r_i$.

@@

```{=latex}
\begin{equation}
f_{\beta}(x) = \frac{\beta}{2\Gamma\left(1 / \beta \right)} e^{-\left| x \right|^\beta}
\end{equation}
```
Here, $\Gamma$ is the gamma function, and $\beta$ is a strictly positive shape parameter. For $\beta = 1$, the probability density function describes a Laplace distribution. A normal distribution is found for $\beta=2$, and for large $\beta$, the distribution approaches a uniform distribution. We will refrain from introducing scale and location parameters here directly.

@@

```{=latex}
\begin{equation}
F_{\alpha}^{-1}(p; \mu, \sigma, \beta) =
\begin{cases}
\mu + \frac{\sigma}{1 - \alpha} F_{\beta}^{-1} \left( \frac{p}{2 \alpha}\right) & \text{, } p \leq \alpha \\
\mu + \frac{\sigma}{\alpha} F_{\beta}^{-1} \left( \frac{1 + p - 2 \alpha}{2 \left(1 - \alpha \right)} \right) & \text{, } p > \alpha
\end{cases}
\end{equation}
```
The quantile function for the asymmetric generalised normal distribution $F_{\alpha}^{-1}$ thus incorporates the quantile function $F_{\beta}^{-1}$ of the symmetric generalised normal distribution. $F_{\beta}^{-1}$ was derived by Griffin to be [@Griffin2018-bf]:

@@

Let central normality be defined as the normality of central portion $\kappa$ of the data, i.e. $\mathbf{X}_{\text{central}} = \left\{x_i \in \mathbf{X} \, | \,  \frac{1-\kappa}{2} \leq  p_i \leq \frac{1 + \kappa}{2}\right\}$, with $p_i$ probabilities of the empirical distribution, as previously.
We then compute the residual errors between the z-scores of the transformed feature $\phi^{\lambda, x_0, s} (\mathbf{X})$ and the expected z-scores from a standard normal distribution: $r_i =\left| \left( \phi^{\lambda, x_0, s}(x_i) - \mu_M)\right) / \sigma_M - F^{-1}_{\mathcal{N}}(p_i) \right|$, with $\mu_M$ and $\sigma_M$ robust Huber M-estimates of location and scale of the transformed feature $\phi^{\lambda, x_0, s} (\mathbf{X})$ [@Huber1981-su].
The set of residual errors for the central portion of the data is then $\mathbf{R}_{\text{central}} = \left\{ r_i \in \left\{ r_1, r_2, \ldots, r_n\right\} \, | \,  \frac{1-\kappa}{2} \leq  p_i \leq \frac{1 + \kappa}{2}\right\}$.

@@

To use the test statistic, the central portion of the data needs to be defined and the Type 1 error rates determined.
We will do so in the [Simulation](#simulation) section.

@@

We used simulated data to assess invariance to location and scale of the proposed power transformations, weighting for robust transformations, and to develop the empirical central normality test.
The $\lambda$ parameter for conventional power transformations (Eqn. \ref{eqn:box-cox-original} and \ref{eqn:yeo-johnson-original}), as well as $\lambda$, $x_0$ and $s$ parameters for location- and scale-invariant power transformations (Eqn. \ref{eqn:box-cox-invariant} and \ref{eqn:yeo-johnson-invariant}) were estimated using the BOBYQA algorithm for derivative-free bound constraint optimisation [@Powell2009-zb] through maximum likelihood estimation.
The required algorithms were implemented in the `power.transform` R software package **ADD REFERENCE**.
Of note, the `power.transform` package shifts feature values into the positive domain if negative or zero values are present for Box-Cox power transformations.

@@

To assess whether the proposed power transformations lead to values of $\lambda$ that are invariant to location and scale of the distribution, we simulated three different distributions.
We first randomly drew $10000$ values from a normal distribution: $\mathbf{X}_{\text{normal}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{N}\left(0, 1\right)$, or equivalently $\mathbf{X}_{\text{normal}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.5, 2\right)$.
The second distribution was a right-skewed generalised normal distribution $\mathbf{X}_{\text{right}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.2, 2\right)$.
The third distribution was a left-skewed generalised normal distribution $\mathbf{X}_{\text{left}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.8, 2\right)$.
We then computed transformation parameter $\lambda$ using the original definitions (Eqn. \ref{eqn:box-cox-original} and \ref{eqn:yeo-johnson-original}) and the location- and scale-invariant definitions (Eqn. \ref{eqn:box-cox-invariant} and \ref{eqn:yeo-johnson-invariant}) for each distribution.
To assess location invariance, a positive value $d_{\text{shift}}$ was added to each distribution with $d_{\text{shift}} \in [1, 10^6]$.
Similarly, to assess scale invariance, each distribution was multiplied by a positive value $d_{\text{scale}}$, where $d_{\text{scale}} \in [1, 10^6]$.

@@

Outlier values were then drawn to randomly replace a fraction of the values of $\mathbf{X}_i$.
This was repeated $m_{\text{out}} = 10$ times, with outlier fractions regularly spaced in $[0.00, 0.10]$.
Thus up to 10 percent of the values could be replaced by outliers.
Outlier values were set according to @Tukey1977-xm, as follows.
Let $x^{*} \sim U\left(-2, 2\right)$.
Then the corresponding outlier value was:

@@

$Q_1$, $Q_3$ and $\text{IQR}$ are the first quartile, third quartile and interquartile range of $\mathbf{X}_i$, respectively.
Outlier values randomly replaced values in $\mathbf{X}_i$ to create $\mathbf{X}_{i,j}$, with $j \in \left\{ 1, \ldots, m_{\text{out}} \right\}$

@@

```{=latex}
\begin{equation}
\label{eqn:minimisation-weighting}
\left\{ \hat{\delta}_1, \hat{\delta}_2 \right\} = \argmin_{\delta_1, \delta_2} \sum_{i=1}^{m_d} \sum_{j=1}^{m_{\text{out}}} \left| \lambda_r \left(\mathbf{X}_{i, j}; \delta_1, \delta_2 \right) - \lambda_0 \left(\mathbf{X}_i \right) \right|
\end{equation}
```
